### 2019-04-17 2-Chapters/1-Chapter/chapter1.tex
Okay for chapters and parts
Small modifications on all chapters
Work work work...

% First chapter begins here
\chapter{Introduction}
\label{chapter:1}
\minitoc
\newpage
% Write miniTOC just after the title
\graphicspath{{2-Chapters/1-Chapter/Images/}}

@@

\begin{itemize}
\item
    \emph{GNU Radio Implementation of MALIN: ``Multi-Armed bandits Learning for Internet-of-things Networks''},
    by \textbf{Lilian Besson}, Rémi Bonnefoi \& Christophe Moy.
    \emph{Wireless Communication and Networks Conference} (IEEE WCNC, \texttt{wcnc2019.ieee-wcnc.org}), Marrakech, Morocco, April 2019,
    \texttt{hal.inria.fr/hal-02006825}.

\item
    \emph{Multi-Player Bandits Revisited},
    by \textbf{Lilian Besson} \& Emilie Kaufmann.
    \emph{Algorithmic Learning Theory} (ALT, \texttt{www.cs.cornell.edu/conferences/alt2018}), Lanzarote, Spain, April 2018,
    \texttt{hal.inria.fr/hal-01629733}.

\item
    \emph{Aggregation of Multi-Armed Bandits learning algorithms for Opportunistic Spectrum Access},\\
    by \textbf{Lilian Besson}, Emilie Kaufmann \& Christophe Moy.
    \emph{Wireless Communication and Networks Conference} (IEEE WCNC, \texttt{wcnc2018.ieee-wcnc.org}), Barcelone, Spain, April 2018,
    \texttt{hal.inria.fr/hal-01705292}.

\item
    \emph{Multi-Armed Bandit Learning in IoT Networks and non-stationary settings},
    by Rémi Bonnefoi, \textbf{Lilian Besson}, Christophe Moy, Emilie Kaufmann \& J. Palicot.
    \emph{Conference on Cognitive Radio Oriented Wireless Networks} (CROWNCOM, \texttt{crowncom.org/2017}), Lisboa, Portugal, Septembre $2017$,
    \texttt{hal.inria.fr/hal-01575419},
    \textbf{Best Paper Award}.

@@

% =============================================================================
\subsection{Submitted works or in progress works waiting for a new submission}

\begin{itemize}
\item
    \emph{The Generalized Likelihood Ratio Test meets klUCB: an Improved Algorithm for Piece-Wise Non-Stationary Bandits},
    by \textbf{Lilian Besson} \& Emilie Kaufmann, February $2019$,
    \texttt{hal.inria.fr/hal-02006471}.

\item
    \emph{Upper-Confidence Bound for Channel Selection in LPWA Networks with Retransmissions},\\
    by Rémi Bonnefoi, \textbf{Lilian Besson}, J. Manco-Vasquez \& Christophe Moy.
    Submitted for MOTIoN workshop (\texttt{sites.google.com/view/wcncworkshop-motion2019}), February $2019$.

\item
    \emph{SMPyBandits: an Open-Source Research Framework for Single and Multi-Players Multi-Arms Bandits (MAB) Algorithms in Python},
    by \textbf{Lilian Besson}, active development since October $2016$,
    \texttt{hal.inria.fr/hal-01840022}.
    About $40000$ lines of code, hosted on \texttt{GitHub.com/SMPyBandits},
    with a complete documentation on \texttt{SMPyBandits.rtfd.io}.

\item
    \emph{What Doubling-Trick Can and Can't Do for Multi-Armed Bandits},\\
    by \textbf{Lilian Besson} \& Emilie Kaufmann, September $2018$,
    \texttt{hal.inria.fr/hal-01736357}.

@@

\item
    \emph{A Note on the Ei Function and a Useful Sum-Inequality},
    by \textbf{Lilian Besson},
    February $2018$,
    \texttt{hal.inria.fr/hal-01847480}.

@@

\paragraph{Seminars} I gave some presentations in the following events:
    SequeL team seminar at Inria Lille in September and December $2017$, and June $2019$;
    SCEE team seminar at CentraleSupélec, Rennes campus, in October $2017$, February $2018$ and June $2019$;
    as well as
    for the GDR ISIS day held in Issy-les-Moulineaux on November $2017$,
    for the brown-bag seminar at ENSAI in Bruz in January $2018$,
    for the weekly CMAP seminar at École Polytechnique in October $2018$.

@@

\paragraph{Training}
    I was also in charge of ``GouTP'' training sessions for about $30$ PhD students at CentraleSupélec Rennes.
    We had a lot of various $1$h training sessions between January $2017$ and June $2019$,
    and I gave about $10$ training, on various topics including Python, \texttt{git}, HAL and arXiv, the Julia language and Bib\TeX{}.

@@

\paragraph{Responsabilities}
    president of the PhD Students Association of IETR lab (ADDI, \texttt{addi.asso.insa-rennes.fr}) in $2017$.
    I was notably in charge of organizing the PhD Students day at Rennes, in June $2017$, with about $350$ people, and presentation of a research poster\footnote{Cf. \texttt{hal.inria.fr/hal-02013839/document}}.
    I also helped for the organization and presented another poster\footnote{Cf. \texttt{hal.inria.fr/hal-02013847/document}} at IETR seminar (\texttt{seminar-ietr-18.sciencesconf.org}), held in Vannes in June $2018$.

\paragraph{Reviews}
	for \emph{European Workshop on Reinforcement Learning} (Lille) \texttt{ewrl.wordpress.com/ewrl14-2018}, in October $2018$, I reviewed $5$ papers.
	I helped colleagues for articles submitted at international conferences \emph{AISTATS} $2019$, \href{https://nips.cc/Conferences/2018/}{\emph{NeurIPS}} $2017$ et $2018$, and \emph{COLT} $2018$ and $2019$, for about 10 \emph{reviews}.

\paragraph{System Administrator}
	maintaining our workstations running GNU/Linux and Windows
	at SCEE team,
	and our cognitive radio test-bed using USRP cards and the GNU Radio software,
	from January $2017$ to June $2019$.

>>>>

% First chapter begins here
\chapter{Setting of This Thesis}
\label{chapter:1}
\minitoc

Abstract for Chapter 1.

\newpage
% Write miniTOC just after the title
\graphicspath{{2-Chapters/1-Chapter/Images/}}

@@

\begin{itemize}
\item
    \emph{GNU Radio Implementation of MALIN: ``Multi-Armed bandits Learning for Internet-of-things Networks''},
    by \textbf{Lilian Besson}, Rémi Bonnefoi \& Christophe Moy.
    \emph{Wireless Communication and Networks Conference} (IEEE WCNC, \texttt{wcnc2019.ieee-wcnc.org}), Marrakech, Morocco, April 2019,
    \texttt{HAL.Inria.fr/hal-02006825}.

\item
    \emph{Multi-Player Bandits Revisited},
    by \textbf{Lilian Besson} \& Emilie Kaufmann.
    \emph{Algorithmic Learning Theory} (ALT, \texttt{www.cs.cornell.edu/conferences/alt2018}), Lanzarote, Spain, April 2018,
    \texttt{HAL.Inria.fr/hal-01629733}.

\item
    \emph{Aggregation of Multi-Armed Bandits learning algorithms for Opportunistic Spectrum Access},\\
    by \textbf{Lilian Besson}, Emilie Kaufmann \& Christophe Moy.
    \emph{Wireless Communication and Networks Conference} (IEEE WCNC, \texttt{wcnc2018.ieee-wcnc.org}), Barcelone, Spain, April 2018,
    \texttt{HAL.Inria.fr/hal-01705292}.

\item
    \emph{Multi-Armed Bandit Learning in IoT Networks and non-stationary settings},
    by Rémi Bonnefoi, \textbf{Lilian Besson}, Christophe Moy, Emilie Kaufmann \& J. Palicot.
    \emph{Conference on Cognitive Radio Oriented Wireless Networks} (CROWNCOM, \texttt{crowncom.org/2017}), Lisboa, Portugal, Septembre $2017$,
    \texttt{HAL.Inria.fr/hal-01575419},
    \textbf{Best Paper Award}.

@@

% =============================================================================
\subsection{Publications in international conferences without proceedings}

\begin{itemize}

\item
    \emph{Upper-Confidence Bound for Channel Selection in LPWA Networks with Retransmissions},\\
    by Rémi Bonnefoi, \textbf{Lilian Besson}, J. Manco-Vasquez \& Christophe Moy.
    Presented at the 1st International MOTIoN workshop (\texttt{sites.google.com/view/wcncworkshop-motion2019}),
    at \emph{Wireless Communication and Networks Conference} (IEEE WCNC, \texttt{wcnc2019.ieee-wcnc.org}), Marrakech, Morocco, April 2019,

@@

% =============================================================================
\subsection{Submitted works}

\begin{itemize}
\item
    \emph{Analyse non asymptotique d'un test séquentiel de détection de ruptures et application aux bandits non stationnaires} (in French),
    submitted at GRETSI 2019, \texttt{GRETSI.fr/colloque2019},
    by \textbf{Lilian Besson} \& Emilie Kaufmann, March $2019$,
    \texttt{HAL.Inria.fr/hal-02006471}.

\item
    \emph{The Generalized Likelihood Ratio Test meets klUCB: an Improved Algorithm for Piece-Wise Non-Stationary Bandits},
    submitted at COLT 2019, \texttt{LearningTheory.org/colt2019/},
    by \textbf{Lilian Besson} \& Emilie Kaufmann, February $2019$,
    \texttt{HAL.Inria.fr/hal-02006471}.

% =============================================================================
\subsection{In progress works waiting for a new submission}

\begin{itemize}
\item
    \emph{SMPyBandits: an Open-Source Research Framework for Single and Multi-Players Multi-Arms Bandits (MAB) Algorithms in Python},
    by \textbf{Lilian Besson}, active development since October $2016$,
    \texttt{HAL.Inria.fr/hal-01840022}.
    About $40000$ lines of code, hosted on \texttt{GitHub.com/SMPyBandits},
    with a complete documentation on \texttt{SMPyBandits.rtfd.io}.

\item
    \emph{What Doubling-Trick Can and Can't Do for Multi-Armed Bandits},\\
    by \textbf{Lilian Besson} \& Emilie Kaufmann, September $2018$,
    \texttt{HAL.Inria.fr/hal-01736357}.

% =============================================================================
\subsection{Other works}

\begin{itemize}
\item
    \emph{A Note on the Ei Function and a Useful Sum-Inequality},
    by \textbf{Lilian Besson},
    February $2018$,
    \texttt{HAL.Inria.fr/hal-01847480}.

@@

\paragraph{Seminars}
    I gave some presentations in the following events:
    SequeL team seminar at Inria Lille in September and December $2017$, and June $2019$;
    SCEE team seminar at CentraleSupélec, Rennes campus, in October $2017$, February $2018$ and June $2019$;
    as well as
    for the GDR ISIS day held in Issy-les-Moulineaux on November $2017$,
    for the brown-bag seminar at ENSAI in Bruz in January $2018$,
    for the weekly seminar at CMAP lab at École Polytechnique in October $2018$,
    for the weekly seminar of the PANAMA project-team at IRISA / Inria Rennes in May $2019$.

@@

\paragraph{Training}
    I was also in charge of ``GouTP'' training sessions for about $30$ PhD students at CentraleSupélec Rennes.
    We had a lot of various $1$h training sessions between January $2017$ and June $2019$,
    and I gave about $12$ training sessions, on various topics including Python, \texttt{git}, HAL and arXiv, the Julia language and Bib\TeX{}.

@@

\paragraph{Responsabilities}
    I was the president of the PhD Students Association of IETR lab (ADDI, \texttt{addi.asso.insa-rennes.fr}) in $2017$.
    I was notably in charge of organizing the PhD Students day at Rennes, in June $2017$, with about $350$ people, and presentation of a research poster\footnote{Cf. \texttt{HAL.Inria.fr/hal-02013839/document}}.
    I also helped for the organization and presented another poster\footnote{Cf. \texttt{HAL.Inria.fr/hal-02013847/document}} at IETR seminar (\texttt{seminar-ietr-18.sciencesconf.org}), held in Vannes in June $2018$.

\paragraph{Reviews}
	for \emph{European Workshop on Reinforcement Learning} (Lille) \texttt{ewrl.wordpress.com/ewrl14-2018}, in October $2018$, I reviewed $5$ papers.
	I helped colleagues for articles submitted at international conferences \emph{AISTATS} $2019$, \emph{NeurIPS} $2017$ et $2018$, and \emph{COLT} $2018$ and $2019$, for about 10 \emph{reviews}.

\paragraph{System Administrator}
	maintaining our workstations running GNU/Linux and Windows
	at SCEE team,
	and our cognitive radio test-bed using USRP cards and the GNU Radio software,
	from January $2017$ to September $2018$.

### 2019-04-17 2-Chapters/5-Chapter/ALT_2018__MPBandits.git/mpBandits.tex
Work work work...

% for N in 4 100; do for M in 3 6 9; do DEBUG=True SAVEALL=False NOPLOTS=True M=$M K=30 N_JOBS=-1 N=$N T=10000 make moremultiplayers; echo "Done for N=$N and M=$M"; read; done; echo "Done for N=$N"; read; done
% TODO run the simulations with N=100 and not N=4
\begin{table}[ht]
  % \begin{footnotesize}
      \centering
      \begin{tabular}{c|ccc}
      \textbf{Algorithm} $\;$ \textbackslash $\;$ Number of players & $M=3$ & $M=6$ & $M=9$ \\
          \hline
          Centralized multiple-play \UCB{} & $317 \pm 37$ & $219 \pm 17$ & $0$ \\
          Centralized multiple-play \klUCB{} & $94 \pm 32$ & $77 \pm 7$ & $0$ \\
          \hline
          \Selfish-\UCB{} & $1175 \pm 70$ & $3705 \pm 379$ & $12709 \pm 246$ \\
          \Selfish-\klUCB{} & $230 \pm 34$ & $673 \pm 48$ & $2689 \pm 230$ \\
          \hline
          \RhoRand-\UCB{} & $1534 \pm 145$ & $4797 \pm 319$ & $12047 \pm 1056$ \\
          \RhoRand-\klUCB{} & $349 \pm 58$ & $2688 \pm 469$ & $6709 \pm 1186$ \\
          \hline
          \RandTopM-\UCB{} & $1074 \pm 36$ & $2751 \pm 229$ & $252 \pm 150$ \\
          \RandTopM-\klUCB{} & $245 \pm 30$ & $1181 \pm 100$ & $617 \pm 592$ \\
          \hline
          \MCTopM-\UCB{} & $941 \pm 23$ & $1368 \pm 86$ & $46 \pm 5$ \\
          \MCTopM-\klUCB{} & $\mathbf{277 \pm 12}$ & $\mathbf{391 \pm 70}$ & $\mathbf{50 \pm 11}$ \\
          \hline
      \end{tabular}
      \caption{Using \klUCB{} is much more efficient than using \UCB{}, for multi-player bandit (here in a simple problem with $K=9$ arms).}
      \label{table:5:comparisonUCB_klUCB}
  % \end{footnotesize}
  \end{table}

@@

Experiments with a different problem for each repetition,
that is uniformly sampled $\boldsymbol{\mu} \sim \cU([0,1]^K)$,
are also considered, in Figure~\ref{fig:5:MP__K9_M6_T5000_N500__4_algos__all_RegretCentralized__BayesianProblems} and \ref{fig:5:MP__K9_M2_T5000_N500__4_algos__all_RegretCentralized__BayesianProblems}.
This helps to check that no matter the \emph{complexity} of the considered problem (one measure of complexity being the constant in our lower bound),
\MCTopM{} performs similarly or better than all the other algorithms,
and \Selfish{} outperforms \rhoRand{} in most cases.
Figure~\ref{fig:5:MP__K9_M6_T5000_N500__4_algos__all_RegretCentralized__BayesianProblems} is a good example
of outstanding performances of \MCTopM{} and \Selfish{} in comparison to \rhoRand{}.
%
Empirically, our proposals were found to almost always outperform \rhoRand{}, and except for \Selfish{} that can fail badly on problems with small $K$,
we verified that \MCTopM{} outperforms the state-of-the-art algorithms in many different problems, and is more and more efficient as $M$ and $K$ grows.

>>>>

% for N in 4 100; do for M in 3 6 9; do DEBUG=True SAVEALL=False NOPLOTS=True M=$M K=30 N_JOBS=-1 N=$N T=10000 make moremultiplayers; echo "Done for N=$N and M=$M"; read; done; echo "Done for N=$N"; read; done
%
\begin{table}[ht]
  % \begin{footnotesize}
      \centering
      \begin{tabular}{c|ccc}
      \textbf{Algorithm} $\;$ \textbackslash $\;$ Number of players & $M=3$ & $M=6$ & $M=9$ \\
          \hline
          Centralized multiple-play \UCB{} & $321 \pm 30$ & $233 \pm 25$ & $0$ \\
          Centralized multiple-play \klUCB{} & $94 \pm 17$ & $68 \pm 18$ & $0$ \\
          \hline
          \Selfish-\UCB{} & $1263 \pm 157$ & $3694 \pm 387$ & $12420 \pm 404$ \\
          \Selfish-\klUCB{} & $243 \pm 31$ & $743 \pm 113$ & $3005 \pm 492$ \\
          \hline
          \RhoRand-\UCB{} & $1455 \pm 208$ & $4775 \pm 463$ & $11794 \pm 1083$ \\
          \RhoRand-\klUCB{} & $394 \pm 96$ & $2385 \pm 412$ & $7057 \pm 1053$ \\
          \hline
          \RandTopM-\UCB{} & $1020 \pm 92$ & $2899 \pm 418$ & $470 \pm 346$ \\
          \RandTopM-\klUCB{} & $258 \pm 43$ & $902 \pm 234$ & $551 \pm 520$ \\
          \hline
          \MCTopM-\UCB{} & $980 \pm 76$ & $1466 \pm 132$ & $43 \pm 13$ \\
          \MCTopM-\klUCB{} & $\mathbf{248 \pm 40}$ & $\mathbf{410 \pm 54}$ & $\mathbf{42 \pm 10}$ \\
          \hline
      \end{tabular}
      \caption{Using \klUCB{} is much more efficient than using \UCB{}, for multi-player bandit (here in a simple problem with $K=9$ arms).}
      \label{table:5:comparisonUCB_klUCB}
  % \end{footnotesize}
  \end{table}

@@

Experiments with a different problem for each repetition,
that is uniformly sampled $\boldsymbol{\mu} \sim \cU([0,1]^K)$,
are also considered, in Figure~\ref{fig:5:MP__K9_M6_T5000_N500__4_algos__all_RegretCentralized__BayesianProblems} and \ref{fig:5:MP__K9_M2_T5000_N500__4_algos__all_RegretCentralized__BayesianProblems}.
This helps to check that no matter the \emph{complexity} of the considered problem (one measure of complexity being the constant in our lower bound),
\MCTopM{} performs similarly or better than all the other algorithms,
and \Selfish{} outperforms \rhoRand{} in most cases.
Figure~\ref{fig:5:MP__K9_M6_T5000_N500__4_algos__all_RegretCentralized__BayesianProblems} is a good example
of outstanding performances of \MCTopM{} and \Selfish{} in comparison to \rhoRand{}.
%
Empirically, our proposals were found to always outperform \rhoRand{}, and except for \Selfish{} that can fail badly on problems with small $K$,
we verified that \MCTopM{} outperforms the state-of-the-art algorithms in many different problems, and is more and more efficient as $M$ and $K$ grows.

### 2019-04-17 2-Chapters/5-Chapter/chapter5.tex
Work work work...

One can observe in Table~\ref{table:5:meanRegretSimulationsEstimatingM} the empirical performances of different algorithms in an example problem, in each case of low, medium and maximum number of players ($M=3,6,9$ for $K=9$ arms).
The three algorithms \RhoRand, \RandTopM{} and \MCTopM{} all suffer from similar costs on their regret when they have to estimate $M$ on the fly (written ``Estimate $M$'' in red, in Table~\ref{table:5:meanRegretSimulationsEstimatingM}). Our proposals are still much more efficient than \RhoRand{} when using the procedure to estimate $M$ described from \cite{Anandkumar11}.
For the two non-extreme cases ($M=3,6$), the performance drop when having to estimate $M$ is quite large (on the three algorithms and two cases, about $\times 3.4$), and consistent on the different algorithm.
The extreme case of $M=K$ players is of highest interest, as \MCTopM{} achieves a very small regret (proved to be $\smallO{\log(T)}$ as it is just the expected time of the orthogonalization process), while the same algorithm with unknown $M$ suffers from a much larger regret.
In this extreme case, \RhoRand{} and its extension both perform very closely, as expected.
%
Additional simulations, for increasing time horizons $T$, confirmed the expected order-optimal regret of this extension of our proposal \MCTopM-\klUCB.

>>>>

One can observe in Table~\ref{table:5:meanRegretSimulationsEstimatingM} the empirical performances of different algorithms in an example problem, in each case of low, medium and maximum number of players ($M=3,6,9$ for $K=9$ arms).
The three algorithms \RhoRand, \RandTopM{} and \MCTopM{} all suffer from similar increase on their regret when they have to estimate $M$ on the fly (written ``Estimate $M$'' in red, in Table~\ref{table:5:meanRegretSimulationsEstimatingM}). Our proposals are still much more efficient than \RhoRand{} when using the procedure to estimate $M$ described from \cite{Anandkumar11}.
For the two non-extreme cases ($M=3,6$), the performance drop when having to estimate $M$ is quite large (on the three algorithms and two cases, about $\times 3.4$), and consistent on the different algorithm.
The extreme case of $M=K$ players is of highest interest, as \MCTopM{} achieves a very small regret (proved to be $\cO(1)$ as it is just the expected time of the orthogonalization process), while the same algorithm with unknown $M$ suffers from a much larger regret.
In this extreme case, \RhoRand{} and its extension both perform very closely, as expected, and much worse than \MCTopM.
%
Additional simulations, for increasing time horizons $T$, confirmed the expected order-optimal regret of this extension of our proposal \MCTopM-\klUCB.

### 2019-04-17 3-Appendices/2-Appendix/appendix2.tex
Ok for tex root
Still fighting against my template...
Work work work...

%!TEX root = ../thesis.tex
% ******************************* Thesis Appendix B ****************************
\chapter{Appendix for Chapter \ref{chapter:2}}
\label{app:chapt2}

In this appendix, blabla.

>>>>

%!TEX root = ../PhD_thesis__Lilian_Besson
% ******************************* Thesis Appendix B ****************************
\chapter{About another publication: ``What Doubling-Trick Can and Can't Do for Multi-Armed Bandits''}
\label{app:2:DoublingTricks}

This appendix quickly presents the contributions of another publication that was not presented in the main text of this thesis, \cite{Besson2018DoublingTricks}.

% \TODOL{
% I cannot include it raw without more work on the maths, we have to write only the best versions of our results.

% But I am interested in including this article in my thesis, mainly because GLRklUCB in Chapter 6 is not anytime!

% I need to try DoublingTrick + GLRklUCB, at least experimentally!
% For the theoretical analysis, it will probably be a huge failure.
% }

As introduced in Chapter~\ref{chapter:2},
an online reinforcement learning algorithm is \emph{anytime} if it does not need to know in advance the horizon $T$ of the experiment.
%
Depending on the context of the practical application of interest, it might be unrealistic to assume to know in advance $T$. We give two examples to illustrate where this prior knowledge can be realistic or not.
On the first hand, consider clinical trials: it is likely that the number of patients is known before starting the trial, and for instance we refer to all the research that studies the setting of fixed-time best-arm identification \cite{audibert2010best,Garivier16BAI}.
On the second hand, consider cognitive radio and decentralized MAB learning implemented on IoT devices: usually a learning step corresponds to an uplink and then downlink message sent and received by the IoT device, and so the time horizon $T$ denotes the total number of such messages. While it can be assumed that the device will run for instance for $10$ years (as it is advertised by some companies), many kinds of applications such as medical sensors or connected fields cannot predict the number of total communications before setting up the device.

For this later range of applications, it is of highest interest to be able to use low-cost MAB algorithms that do not rely on prior knowledge of the problem for which they will be applied, and especially do not need to know the horizon $T$.
While we proposed in Chapter~\ref{chapter:5} any-time algorithms solving the presented problem of stationary multi-player bandit, our solution for the problem of non-stationary MAB problem studied in Chapter~\ref{chapter:6} does rely on a prior knowledge of the horizon $T$.
It is interesting to know what is the best approach to fix this weakness: work more and design algorithms that are inherently any-time, or use a generic technique to avoid depending on a prior knowledge of $T$, and automatically transform our non-anytime approach to make it anytime.

A well-known technique to obtain an anytime algorithm from any non-anytime algorithm is the ``Doubling Trick'', as first introduced in \cite{CesaLugosi06}.
We studied doubling tricks between fall 2017 and spring 2018, and we wrote an article \cite{Besson2018DoublingTricks} which was rejected at the COLT 2018 conference, and unfortunately we lacked the time to improve it and resubmit it to another conference.
%
In the context of adversarial or stochastic multi-armed bandits,
the performance of an algorithm is measured by its regret,
and we study two families of sequences of growing horizons (geometric and exponential)
to generalize previously known results that certain doubling tricks can be used to conserve certain regret bounds.
In a broad setting, we prove that a geometric doubling trick can be used to conserve (minimax) bounds in $R_T = \cO(\sqrt{T})$ but \emph{cannot} conserve (distribution-dependent) bounds in $R_T = \cO(\log T)$.
We give insights as to why exponential doubling tricks may be better, as they conserve bounds in $R_T = \cO(\log T)$, and are close to conserving bounds in $R_T = \cO(\sqrt{T})$.
Interestingly, we prove that they conserve bounds of the mixed form $R_T = \cO(T^{\gamma} (\log(T))^{\delta})$, for $0<\gamma<1$ and $\delta>0$, and so an exponential doubling trick could be used to obtain an anytime version of the algorithm we propose for non-stationary bandits, \GLRklUCB{} in Chapter~\ref{chapter:6}.
However, our study was only focussing on stationary bandit, and it is left as a future work to explore the harder case of piece-wise stationary problems.

In our article \cite{Besson2018DoublingTricks}, we also present numerical experiments in the case of stationary MAB problems, to compare the performance of efficient anytime algorithms, like \klUCB, against efficient non-anytime algorithms, like \KLUCBpp, made anytime with different doubling-trick.
We conclude that for such problems, if $T$ is not known before, it is always more efficient to use policies that were designed to be anytime that to use a doubling trick.
For example, an applicative paper written in 2018, \cite{li2019useDoublingTrick}, only tested the use of an exponential doubling trick combined with \KLUCBpp, but most surely the \klUCB{} algorithm would have given better empirical performance as well as more robust results.

To conclude this work, we would need to complete the study of the doubling tricks, and instead of focussing on two families of doubling tricks (geometric and exponential), we need to completely characterize the doubling tricks that allow to preserve certain regret bound.
Such doubling is given either by the function mapping the current time $t$ to the current estimate of the horizon $T(t)$, or the sequence $(T_i)_{i\in\N^*}$ of successive estimates of the horizons.
We are interested in pursuing this work, in the hope of finding an intermediate sequence, growing faster than a geometric but slower than an exponential doubling sequence, that can preserve both worlds, problem-dependent bounds in $\cO(\log(T))$ and problem-independent bounds in $\cO(\sqrt{T})$.
